Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-23 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
More related work

In all these systems, the evolutionary interactive process is captured by the system. The genetic lineage of each
individual is presented where users can visualize the relationships between them and evolutionary operators used in
their creation. Also there is information regarding users and their collaborations.  Common offerings show 
interesting individuals order by categories, number of votes, best of the week among others.

These features have the goal of encouraging participation but require the use of a database system 
for their implementation. Picbreeder \cite{picbreeder} is implemented with a service oriented
architecture using a relational database and the file system for genotypes and images.

>>>>

In all these systems, the evolutionary interactive process is captured by the system. The genetic lineage of each
individual is presented where users can visualize the relationships between them and evolutionary operators used in
their creation. Also there is information regarding users and their collaborations.  Common offerings show 
interesting individuals order by categories, number of votes, best of the week among others.
These features have the goal of encouraging participation but require the use of a database system 
for their implementation. Picbreeder \cite{picbreeder} is implemented with a service oriented
architecture using a relational database and the file system for genotypes and images.

Collaborative IEC systems need to store highly connected data, as it is common in current applications
like social networks, and the world wide web. In order to deal with large datasets of connected data,
graph databases \cite{angles2012comparison} have been proposed as an alternative to relational databases 
which have performance limitations when dealing with highly connected data \cite{holzschuher2013performance}.

The present work builds on a previous proposals and extends the C-IEA approach.
First, it proposes a graph data model for representing the interactive process of C-IEC systems.
Second, it incorporates the graph model to the evolutionary algorithm.
Finally, uses the same model to increase the collaboration of volunteers.
